Global Deaths Due to Air Pollution

### 2022-05-01 outline.Rmd
made the plots interactive for average death count

# Which country has the highest death count?

@@

Here's a graph to clearly visualize the previous table
```{r}
#Plot High Population Deaths (average)
ggplot(deaths_highpop_countries)+
  geom_col(mapping = aes(x=country, y=average_death_high))+
             xlab("Country")+
             ylab("Average deaths (per 100,000)")+
             ggtitle("Average total deaths in high-population countries")+
  coord_flip()

#Plot of Low Population Deaths (average)
ggplot(deaths_lowpop_countries)+
  geom_col(mapping = aes(x=country, y=average_death_low))+
             xlab("Country")+
             ylab("Average deaths (per 100,000)")+
             ggtitle("Average total deaths in low-population countries")+
  coord_flip()
```

# Which type of pollution has the greatest number of deaths?
# Pollution Over Time 
## Which year had the worst pollution?
## Which year had the worst indoor? Outdoor particulate? Outdoor ozone? 
# Which is worse - outdoor or indoor pollution?

>>>>

# Death Count
> Which country has the highest death count?

@@

Here's a graph to clearly visualize the previous table
```{r}
#Plot High Population Deaths (average)
h<- ggplot(deaths_highpop_countries)+
  geom_col(mapping = aes(x=country, y=average_death_high))+
             xlab("Country")+
             ylab("Average deaths (per 100,000)")+
             ggtitle("Average total deaths in high-population countries")+
  coord_flip()

ggplotly(h)

#Plot of Low Population Deaths (average)
l <- ggplot(deaths_lowpop_countries)+
  geom_col(mapping = aes(x=country, y=average_death_low))+
             xlab("Country")+
             ylab("Average deaths (per 100,000)")+
             ggtitle("Average total deaths in low-population countries")+
  coord_flip()

ggplotly(l)
```

# Which type of pollution has the greatest number of deaths?

# Pollution Over Time 
## Which year had the worst pollution?
## Which year had the worst indoor? Outdoor particulate? Outdoor ozone? 
# Which is worse - outdoor or indoor pollution?
